---
title: "Topic"
subtitle: "FSH 507 Fall 2019"
author: "Your Name"
date: " `r Sys.Date()`"
output:
  powerpoint_presentation: default
  ioslides_presentation: default
  html_document: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(gapminder)
```

# R Markdown

## Getting Started

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown for presentations see <https://bookdown.org/yihui/rmarkdown/presentations.html>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
pressure %>% 
  ggplot(aes(temperature, pressure)) + 
  geom_point()

```


# Materials



